---
title: "Shiny Application Documentation"
author: "Parvaneh Rezaei"
date: "2026-09-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This R script creates a simple interactive user interface using the Shiny package. The application demonstrates basic Shiny components, including headings, text, an image, and an interactive slider.

## Inputs

The application accepts user input through an interactive slider. The user can move the slider to select a value.

## R Script

The Shiny package is loaded before creating the application.

```{r}
library(shiny)
```

The user interface contains the main elements of the Shiny application.

```{r}
ui <- fluidPage(
  titlePanel("Shiny User Interface Project"),
  
  sidebarLayout(
    sidebarPanel(
      sliderInput(
        "value",
        "Select a value:",
        min = 1,
        max = 100,
        value = 50
      )
    ),
    
    mainPanel(
      h2("Welcome to the Shiny Application"),
      p("Use the slider to select a value."),
      textOutput("selectedValue")
    )
  )
)
```

The server processes the user's slider selection and displays the selected value.

```{r}
server <- function(input, output) {
  output$selectedValue <- renderText({
    paste("Selected value:", input$value)
  })
}
```

The following code starts the Shiny application.

```{r}
shinyApp(ui = ui, server = server)
```

## Outputs

The application displays a Shiny user interface with a title, descriptive text, an interactive slider, and the value selected by the user.

## AI-Assisted Formatting

AI assistance was used to improve the Markdown organization, add clear section headings, and format the R code blocks. The final content and formatting were reviewed for clarity and consistency.